Parametric analysis of ambisonic audio

### 2020-07-28 Chapters/CoherenceEstimation.tex
minor

In this Chapter, we study diffuseness estimation by subjecting a tetrahedral microphone array to spherically isotropic noise fields.
The motivation for this work is, first, that tetrahedral arrays are a well known type of microphone arrays, which have today become popular for applications related to Virtual and Augmented Reality. 
Second, the spherical isotropic sound field is known to be a good approximation to the reverberant part of the sound field in a room \cite{elko_spatial_2001, mccowan_microphone_2003}, and therefore it would be interesting to investigate how different microphone arrays behave under such conditions.

>>>>

In this Chapter, adapted from a previous academic publication \cite{stefanakis2019analysis},  we study diffuseness estimation by subjecting a tetrahedral microphone array to spherically isotropic noise fields.
The motivation for this work is, first, that tetrahedral arrays are a well known type of microphone arrays, which have today become popular for applications related to Virtual and Augmented Reality. 
Second, the spherical isotropic sound field is known to be a good approximation to the reverberant part of the sound field in a room \cite{elko_spatial_2001, mccowan_microphone_2003}, and therefore it would be interesting to investigate how different microphone arrays behave under such conditions.

### 2020-07-28 Chapters/Conclusions.tex
minor

	\textbf{"Analysis of spherical isotropic noise fields with an A-Format tetrahedral microphone"}.
	\underline{A. P\'erez-L\'opez} and N. Stefanakis.
	\textit{The Journal of the Acoustical Society of America 146.4 (2019): EL329-EL334.}

@@

	\textbf{"Blind reverberation time estimation from ambisonic recordings"}.
	\underline{A. P\'erez-L\'opez}, A. Politis and E. G\'omez.
	Submitted to \textit{IEEE 22nd International Workshop on Multimedia Signal Processing, 2020.}\\

	\textbf{"PAPAFIL: a low complexity sound event localization and detection method with parametric particle filtering and gradient boosting".}
	\underline{A. P\'erez-L\'opez} and R. Ibañez-Usach.
	Submitted to \textit{Detection and Classification of Acoustic Scenes and Events 2020 Workshop (DCASE2020)}.\\

	\textbf{"A hybrid parametric-deep learning approach for sound event localization and detection".}
	\underline{A. P\'erez-L\'opez}, E. Fonseca and X. Serra.
	In \textit{Proceedings of the Detection and Classification of Acoustic Scenes and Events 2019 Workshop (DCASE2019)}.

	\textbf{"Ambiscaper: A tool for automatic generation and annotation of reverberant ambisonics sound scenes".}\\
	\underline{A. P\'erez-L\'opez}.
	In \textit{Proceedings of the 16th International Workshop on Acoustic Signal Enhancement (IWAENC). IEEE, 2018.}

@@

	\textbf{"Ambisonics directional room impulse response as a new convention of the spatially oriented format for acoustics".}
	\underline{A. P\'erez-L\'opez} and J. De Muynke.
	In \textit{Proceedings of the 144th Audio Engineering Society Convention. Audio Engineering Society, 2018.}\\

	\textbf{"pysofaconventions, a Python API for SOFA".}
	\underline{A. P\'erez-L\'opez}.
	In \textit{Proceedings of the 148th Audio Engineering Society Convention. Audio Engineering Society, 2020.}\\

	\textbf{"A Python library for multichannel acoustic signal processing".}
	\underline{A. P\'erez-L\'opez} and A. Politis.
	In \textit{Proceedings of the 148th Audio Engineering Society Convention. Audio Engineering Society, 2020.}\\

@@

	 \textbf{"Sound event localization and detection based on CRNN using dense rectangular filters and channel rotation data augmentation".}
	F. Ronchini, D. Arteaga and \underline{A. P\'erez-L\'opez}.
	Submitted to \textit{Detection and Classification of Acoustic Scenes and Events 2020 Workshop (DCASE2020)}.\\

>>>>

	\textbf{"Analysis of spherical isotropic noise fields with an A-Format tetrahedral microphone"}.
	\underline{A. P\'erez-L\'opez} and N. Stefanakis.
	\textit{The Journal of the Acoustical Society of America 146.4 (2019): EL329-EL334.} \cite{stefanakis2019analysis}.

@@

	\textbf{"Blind reverberation time estimation from ambisonic recordings"}.
	\underline{A. P\'erez-L\'opez}, A. Politis and E. G\'omez.
	Submitted to \textit{IEEE 22nd International Workshop on Multimedia Signal Processing, 2020.} \cite{rt}.

	\textbf{"PAPAFIL: a low complexity sound event localization and detection method with parametric particle filtering and gradient boosting".}
	\underline{A. P\'erez-L\'opez} and R. Ibañez-Usach.
	Submitted to \textit{Detection and Classification of Acoustic Scenes and Events 2020 Workshop (DCASE2020)} \cite{papafil}.

	\textbf{"A hybrid parametric-deep learning approach for sound event localization and detection".}
	\underline{A. P\'erez-L\'opez}, E. Fonseca and X. Serra.
In \textit{Proceedings of the Detection and Classification of Acoustic Scenes and Events 2019 Workshop (DCASE2019)} \cite{perez2019hybrid}.

	\textbf{"Ambiscaper: A tool for automatic generation and annotation of reverberant ambisonics sound scenes".}\\
	\underline{A. P\'erez-L\'opez}.
	In \textit{Proceedings of the 16th International Workshop on Acoustic Signal Enhancement (IWAENC). IEEE, 2018} \cite{perez2018ambiscaper}.

@@

	\textbf{"Ambisonics directional room impulse response as a new convention of the spatially oriented format for acoustics".}
	\underline{A. P\'erez-L\'opez} and J. De Muynke.
	In \textit{Proceedings of the 144th Audio Engineering Society Convention. Audio Engineering Society, 2018} \cite{perez2018ambisonics}.

	\textbf{"pysofaconventions, a Python API for SOFA".}
	\underline{A. P\'erez-L\'opez}.
	In \textit{Proceedings of the 148th Audio Engineering Society Convention. Audio Engineering Society, 2020} \cite{pysofaconventions}.

	\textbf{"A Python library for multichannel acoustic signal processing".}
	\underline{A. P\'erez-L\'opez} and A. Politis.
	In \textit{Proceedings of the 148th Audio Engineering Society Convention. Audio Engineering Society, 2020} \cite{perez2020python}.

@@

	 \textbf{"Sound event localization and detection based on CRNN using dense rectangular filters and channel rotation data augmentation".}
	F. Ronchini, D. Arteaga and \underline{A. P\'erez-L\'opez}.
	Submitted to \textit{Detection and Classification of Acoustic Scenes and Events 2020 Workshop (DCASE2020)} \cite{ronchini}. \\

### 2020-07-28 Chapters/DataGeneration.tex
minor

The Multichannel Acoustic Signal Processing (\textit{MASP}) is a Python library consisting of a collection of methods related with acoustics and microphone array processing.
The library is mostly a transcoding from several Matlab libraries by A. Politis\cite{politis2016microphone, github_politis}. 
It can be conveniently installed using \textit{pip}.

@@

Given that the described situation meets all requirements, the \textit{Ambisonics Directional Room Impulse Response} (AmbisonicsDRIR) convention has been therefore proposed as SOFA convention.\\

@@

The library \textit{pysofaconventions} has been created with the aim to provide an alternative to the existing Matlab/Octave and C/C++ implementations. 
For ease of installation, it is integrated in the standard python package manager, \textit{pip}.

@@

\textit{AmbiScaper} is a tool designed to provide a flexible way of creating complex ambisonics sound scenes and their associated groundtruth annotations, to be used in the context of source localization and separation algorithms.
\textit{AmbiScaper} offers a high level control of the sound scene parameters, and provides a simple interface for the creation of large datasets with custom characteristics.
\textit{AmbiScaper} is based on \textit{Scaper}, a framework designed to generate annotations for training Sound Event Detection models \cite{Salamon2017}.\\

>>>>

The Multichannel Acoustic Signal Processing (\textit{MASP}) is a Python library consisting of a collection of methods related with acoustics and microphone array processing \cite{perez2020python}.
The library is mostly a transcoding from several Matlab libraries by A. Politis\cite{politis2016microphone, github_politis}. 
It can be conveniently installed using \textit{pip}.

@@

Given that the described situation meets all requirements, the \textit{Ambisonics Directional Room Impulse Response} (AmbisonicsDRIR) convention has been therefore proposed as SOFA convention \cite{perez2018ambisonics}.\\

@@

The library \textit{pysofaconventions} has been created with the aim to provide an alternative to the existing Matlab/Octave and C/C++ implementations \cite{pysofaconventions}.
For ease of installation, it is integrated in the standard python package manager, \textit{pip}.

@@

\textit{AmbiScaper} \cite{perez2018ambiscaper} is a tool designed to provide a flexible way of creating complex ambisonics sound scenes and their associated groundtruth annotations, to be used in the context of source localization and separation algorithms.
\textit{AmbiScaper} offers a high level control of the sound scene parameters, and provides a simple interface for the creation of large datasets with custom characteristics.
\textit{AmbiScaper} is based on \textit{Scaper}, a framework designed to generate annotations for training Sound Event Detection models \cite{Salamon2017}.\\

### 2020-07-28 Chapters/ReververationTimeEstimation.tex
minor

On the other hand, recent years have witnessed a growing interest in immersive audio for virtual and augmented reality.
This situation has consolidated Ambisonics \cite{zotter2019ambisonics} as the \textit{de facto} standard for spatial audio. Dedicated spherical microphone arrays have reached the market in last years; their multichannel nature makes possible spatial manipulations that 
%improve traditional signal processing methods.
complement traditional signal enhancement methods.

@@

The rest of the chapter is organized as follows. Section~\ref{sec:signalmodel} introduces the nomenclature and the signal model. Sections~\ref{sec:baseline} and \ref{sec:proposed} describe the baseline and the proposed methods, respectively. The experimental setup is described in Section~\ref{sec:experimental}, and the results are discussed in Section~\ref{sec:results}. Finally, a conclusion is presented in Section~\ref{sec:conclusion}.

@@

\begin{figure*}[htbp]
	\centerline{\includegraphics[width=1.3\textwidth]{Figures/ReverberationTimeEstimation/96.png}}
	\caption{Experiment results for \textit{speech} (left column) and \textit{drums} (right column) datasets. Estimation error computed for each audio clip.}
	\label{fig:results1}
\end{figure*}
\begin{figure*}[htbp]
	\centerline{\includegraphics[width=1.2\textwidth]{Figures/ReverberationTimeEstimation/94.png}}
	\caption{Experiment results for \textit{speech} (left column) and \textit{drums} (right column) datasets. Total estimation error across audio clips and acoustic conditions. Top: boxplot. Bottom: histogram and density plot}
	\label{fig:results2}
\end{figure*}

>>>>

On the other hand, recent years have witnessed a growing interest in immersive audio for virtual and augmented reality.
This situation has consolidated Ambisonics as the \textit{de facto} standard for spatial audio. Dedicated spherical microphone arrays have reached the market in last years; their multichannel nature makes possible spatial manipulations that 
%improve traditional signal processing methods.
complement traditional signal enhancement methods.

@@

The rest of the Chapter is organized as follows. Section~\ref{sec:signalmodel} introduces the nomenclature and the signal model. Sections~\ref{sec:baseline} and \ref{sec:proposed} describe the baseline and the proposed methods, respectively. The experimental setup is described in Section~\ref{sec:experimental}, and the results are discussed in Section~\ref{sec:results}. Finally, a conclusion is presented in Section~\ref{sec:conclusion}.

The research presented in this Chapter has been submitted for publication at the IEEE 22nd International Workshop on Multimedia Signal Processing \cite{rt}.

@@

\begin{figure*}[htbp]
	\centerline{\includegraphics[width=1.1\textwidth]{Figures/ReverberationTimeEstimation/96.png}}
	\caption{Experiment results for \textit{speech} (left column) and \textit{drums} (right column) datasets. Estimation error computed for each audio clip.}
	\label{fig:results1}
\end{figure*}
\begin{figure*}[htbp]
	\centerline{\includegraphics[width=1.2\textwidth]{Figures/ReverberationTimeEstimation/94.png}}
	\caption{Experiment results for \textit{speech} (left column) and \textit{drums} (right column) datasets. Total estimation error across audio clips and acoustic conditions. Top: boxplot. Bottom: histogram and density plot}
	\label{fig:results2}
\end{figure*}

### 2020-07-28 Chapters/SELD.tex
minor

Finally, it is important to remark that the method described here is the continuation of an algorithm presented at the DCASE 2019 Challenge \cite{perez2019hybrid}; both algorithms share a common structure and a similar approach to the SELD problem. 
However, the current proposal tries to solve some of the problems identified on our early approach, mainly related with a low frame recall derived from a naive approach to event segmentation. Moreover, the current method also presents a complexity reduction, regarding the single-source 
DOA estimation and the classifier.

>>>>

Finally, it is important to remark that the method described here has been reported in a conference paper submitted to the DCASE Workshop 2020 \cite{papafil},  which in turn describes the improvement of an algorithm presented at the DCASE 2019 Challenge \cite{perez2019hybrid}.

While both algorithms share a common structure and a similar approach to the SELD problem, the current proposal tries to solve some of the problems identified on our early approach, mainly related with a low frame recall derived from a naive approach to event segmentation. Moreover, the current method also presents a complexity reduction, regarding the single-source DOA estimation and the classifier.
